### 2016-01-24 Projects/DelCo_2012/Report/DelCo_2012.tex
update cafs report

The fire suppression series included 14 tests in two single-story experimental structures. Six tests were conducted in the East structure and six tests were conducted in the West structure, each including both water and CAF application as a suppression agent. The nozzle patterns were varied from straight stream to narrow fog. Two additional tests were conduction on suppression tactics for attic fires in residential dwellings, one in each structure. For these tests, a smooth bore nozzle was used.

@@

Two identical concrete structures were built on a concrete slab as shown in Fig.~\ref{fig:Delaware_County,_PA_Fire_Test_Structures}. They were designed to simulate a single floor of a residential structure.  The outer wall of each structure was composed of interlocking concrete blocks 0.61~m (2~ft) wide, 0.61~m (2~ft) high and 1.22~m (4~ft) long.  The interior dimensions of each structure were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high. The joints and gaps between the blocks were filled with high temperature insulation.

@@

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStory}
% 	\caption{Delaware County, PA Fire Test Structure}
% 	\label{fig:DelCoSingleStory}
% \end{figure}

@@

@@

The fire suppression testing included 2 bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, 2 total heat flux gauge pairs, and 2 total heat flux guage/radiometer pairs. Figure~\ref{fig:Fire_Suppression_Instrumentation_Dimensions} provides the positions within the burn room, hallway, and entrance foyer where the senors were located (cf. Fig.~\ref{fig:Instrumentation_Legend} for reference on the symbols). Each bare-bead thermocouple array had 8 thermocouples. The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were space 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling. The three bi-directional probe arrays had unique sensor locations. For the window array there were four sensor pairs located 0.28~m (0.95~ft), 0.58~m (1.90~ft), 0.84~m (2.85~ft), and 1.16~m (3.8~ft) below the soffit. For the hallway array, the 7 sensor pairs started 0.3~m (1~ft) below the ceiling and were spaced every 0.3~m (1~ft) ending 2.13~m (7~ft) below the ceiling. The doorway array also had 7 sensor pairs, but the first sensors were located 0.15~m (0.5~ft) below the soffit. The remaining sensors were spaced every 0.3~m (1~ft) with the bottom pair 1.83~m (6~ft) below the doorway soffit. The total heat flux guage/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling. The pairs of total heat flux guages were set 1~m (3~ft) off the ground with one sense ``looking'' vertical and the other horizontal.

@@

@@

@@

>>>>

The fire suppression series included 18 tests in two single-story experimental structures and one two-story structure. Fourteen tests were conducted in the single story structures (7 tests in each structure) using both water and CAFs application as a suppression agent. The nozzle patterns were varied from straight stream to narrow fog. Two of the tests examined suppression tactics for attic fires in residential dwellings, one in each structure. For the attic tests, a smooth bore nozzle was used. The 4 two-story tests used both water and CAF from a straight-stream nozzle.

@@

Two identical single story concrete structures were built on a concrete slab as shown in Fig.~\ref{fig:Delaware_County,_PA_Fire_Test_Structures}. They were designed to simulate a single floor of a residential structure.  The outer wall of each structure was composed of interlocking concrete blocks 0.61~m (2~ft) wide, 0.61~m (2~ft) high and 1.22~m (4~ft) long.  The interior dimensions of each structure were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high. The joints and gaps between the blocks were filled with high temperature insulation.

@@

@@

The west structure was modified to add second story to be able to test larger fires and remote effects from suppression. The outer walls of the bottom floor of the two-story structure were identical to that of the single story structures described above but with an open floor plan. The interior dimensions were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high. The second story walls were framed with steel studs and track. The studs were set to 0.40~m (16~in) centers.

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCo}
	\caption{Delaware County, PA Fire Two-Story Test Structure}
	\label{fig:delco_2story}
\end{figure}

@@

The fire suppression testing in the single story included 2 bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, 2 total heat flux gauge pairs, and 2 total heat flux guage/radiometer pairs. Figure~\ref{fig:Fire_Suppression_Instrumentation_Dimensions} provides the positions within the burn room, hallway, and entrance foyer where the senors were located (cf. Fig.~\ref{fig:Instrumentation_Legend} for reference on the symbols). Each bare-bead thermocouple array had 8 thermocouples. The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were space 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling. The three bi-directional probe arrays had unique sensor locations. For the window array there were four sensor pairs located 0.28~m (0.95~ft), 0.58~m (1.90~ft), 0.84~m (2.85~ft), and 1.16~m (3.8~ft) below the soffit. For the hallway array, the 7 sensor pairs started 0.3~m (1~ft) below the ceiling and were spaced every 0.3~m (1~ft) ending 2.13~m (7~ft) below the ceiling. The doorway array also had 7 sensor pairs, but the first sensors were located 0.15~m (0.5~ft) below the soffit. The remaining sensors were spaced every 0.3~m (1~ft) with the bottom pair 1.83~m (6~ft) below the doorway soffit. The total heat flux guage/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling. The pairs of total heat flux guages were set 1~m (3~ft) off the ground with one sense ``looking'' vertical and the other horizontal.

@@

Fire suppression testing in the two-story structure included similar types instrumentation but included more sensors. Three bare-bead thermocouple arrays and 2 bi-directional probe plus solid thermocouples arrays were used in the first floor. Fig.~\ref{fig:fire_supp_first_2story} shows the positions of the instrumentation (cf. Fig.~\ref{fig:Instrumentation_Legend} for reference on the symbols). Each of the bare-bead arrays had 8 thermocouples with the same spacing as the single-story tests. The bi-directional probe and solid thermocouple arrays also had 8 sensors with the first probe 0.08~m (0.25~ft) below the soffit with the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Instrumentation}
	\caption{Instrumentation Schematic for the First Floor of Fire Suppression Experiments in Two Story Structure.}
	\label{fig:fire_supp_first_2story}
\end{figure}

The second story featured 6 bare-bead arrays and 3 bi-directional probe plus solid thermocouple arrays. The second floor also had three heat flux sensor pairs (one facing horizontal and one facing vertical) that were 1~m (3~ft) off the ground. Fig.~\ref{fig:fire_supp_second_2story} shows the positions of the instrumentation (cf. Fig.~\ref{fig:Instrumentation_Legend} for reference on the symbols). The bare-bead thermocouple arrays featured 8 sensors with the same spacing as the basement level. The bi-direction probe arrays at the south wall door and at the top of the stairwell were comprised of 8 sensor pairs with the same spacing as the basement level. The third bi-directional probe array (3~m (9~ft) off the North wall and 0.6~m (2~ft) off the East wall) has 8 sensor pairs with the same spacing at the bare-bead thermocouple arrays.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Instrumentation}
	\caption{Instrumentation Schematic for the Second Floor of Fire Suppression Experiments in Two Story Structure.}
	\label{fig:fire_supp_second_2story}
\end{figure}

@@

\paragraph{Single-Story Structures}
\label{sec:suppresion_single}

@@

\paragraph{Two-Story Structures}
\label{sec:suppresion_two}
